### 2023-09-03 sections/5-discussion.tex
merge conflict

In comparison to other methods, While CAKES has perfect recall for distance metrics, it exhibits worse recall under non-metrics (specifically, cosine distance). This bears further investigation, but likely stems from how heavily the knn and clustering algorithms depend on the triangle inequality.
Preliminary results suggest that when FAISS and HNSW are tuned for lower recall, they are still slower than CAKES in all cases.

@@

>>>>

In comparison to other methods, While CAKES has perfect recall for distance metrics, it exhibits worse recall under non-metrics (specifically, cosine distance). This bears further investigation, but likely stems from how heavily the $k$-NN and clustering algorithms depend on the triangle inequality.
Preliminary results suggest that when FAISS and HNSW are tuned for lower recall, they are still slower than CAKES in all cases.

@@

The source code for CAKES is available under an MIT
license at https://github.com/URI-ABD/clam.
